preprocessing

### 2022-11-22 r-prep/prep.Rmd
Created Cumulative CO Emissions data

```

>>>>

```{r}
load("data-raw/data_cumulative_co2.RData")

# need to add filling values when joining
dev_status=data_base %>% 
    group_by(country, year,region_ar6_dev) %>% 
    summarise()

data_hist_co2=data_cumulative_co2 %>% 
  left_join(dev_status, by= c("country","year")) %>% 
  filter(year <= 2019) %>% 
    mutate(
      EU = country %in% eurostat::eu_countries[2]$name,
      woc = country != "China",
      deving_woc = woc & region_ar6_dev == "developing",
      deved = region_ar6_dev == "developed",
      adp_region_woc = woc & region_ar6_6 == "Asia and developing Pacific",
      adp_region_deving_woc = adp_region_woc & deving_woc
    ) %>% 
  select(-woc)

save(data_hist_co2,file="data-transf/data_hist_co2.RData")
```
